Boundary Labeling for annotated documents

### 2018-02-24 LaTeX/Paper.tex
Paper: Added section about routing algorithm's computation time. (TODO: Inspect how leaders influence each other's search space) Program: Changed routing algorithm to properly use DFS - it now remembers nodes that were backtracked through.

>>>>

Next, we shall look at the routing algorithm - since we use depth-first search, which is a well-known algorithm, the worst-case computation time is known to be $|V|+|E|$. To reach this time, we'd have to try and use every single edge in the graph, reaching each of the graph's vertices in the process. However, as our algorithm can't use any edges leading away from its target, our search space is reduced to only the vertices either in lower-numbered $s \in S$ (``above'') or those in the same $s$, but located between the source and the border vertices. If we also take into account that leaders aren't allowed to cross one another, this further limits our search space, removing all vertices above the previous leader's vertices.
